---
title: "Temperature dependence of biomass and ecosystem function depend on species interactions. Supplementary File 3: Zooplankton figures and tables."

output:
  pdf_document: default
  html_document: default

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r load librares, echo=FALSE}

### load libraries
library(MuMIn)
library(lme4)
#library(plyr)
library(tidyverse) 
library(broom)
library(reshape2)
library(captioner)
library(knitr)
library(gridExtra)
#library(glmmADMB)
#library(sandwich)
library(tinytex)
```

```{r load data}
data <- read.csv("../data/GarzkeAllwks.csv")
k <- 8.617342*10^-5  # eV/K
xlab <- expression(paste('Temperature (',~degree,'C)',sep=''))
#labels <- c(P = "Algae", PZ = "Algae + Grazers", PZN = "Algae + Grazers + Predators")
```

```{r write functions}
overdisp_fun <- function(model) {
  vpars <- function(m) {
    nrow(m)*(nrow(m)+1)/2
  } 
  model.df <- sum(sapply(VarCorr(model), vpars)) + length(fixef(model))
  rdf <- nrow(model.frame(model))-model.df
  rp <- residuals(model, type = "pearson") # computes pearson residuals
  Pearson.chisq <- sum(rp^2)
  prat <- Pearson.chisq/rdf
  pval <- pchisq(Pearson.chisq, df = rdf, lower.tail = FALSE)
  c(chisq = Pearson.chisq, ratio = prat, rdf = rdf, p = pval)
} 
```

```{r captions}
table_nums <- captioner::captioner(prefix = "Table S3.") #sets prefix for all tables
table_nums(name = "Table_1", caption = "Model selection results for zooplankton abundance, with 1|Tank as a random effect. Model terms are: intercept (Int), Temperature - weekly average (Tw), trophic treatment (TL), statistical estimates", display = FALSE)
table_nums(name = "Table_S3.2", caption = "Daphnia abundance model selection results for Poisson regression. Model terms are: intercept (Int), trophic treatment (TL), Temperature - weekly average (Tw), and statistical estimates", display = FALSE)
table_nums(name = "Table_S3.3", caption = "Daphnia abundance model coefficients", display = FALSE)
table_nums(name = "Table_S3.4", caption = "Copepod abundance model selection results for Poisson regression. Model terms are: intercept (Int), trophic treatment (TL), Temperature - weekly average (Tw), temperature - expt average (Tt), interaction terms and statistical estimates", display = FALSE)
table_nums(name = "Table_S3.5", caption = "Copepod abundance model coefficients", display = FALSE)
table_nums(name = "Table_S3.6", caption = "Zooplankton body size model selection results", display = FALSE)
table_nums(name = "Table_S3.7", caption = "Zooplankton body size model selection results", display = FALSE)
table_nums(name = "Table_S3.8", caption = "Zooplankton body size model selection results. Model terms are: intercept (Int), Temperature - weekly average (Tw), Taxon (Tx), trophic treatment (TL), and statistical estimates", display = FALSE)
table_nums(name = "Table_S3.9", caption = "Zooplankton size model estimates, from table S3.8", display = FALSE)

fig_nums <- captioner::captioner(prefix = "Figure S3.")
fig_nums(name = "Fig_S3.1", caption = "Abundance of zooplankton (Number / 10L) over all tanks and weeks.", display = FALSE)
fig_nums(name = "Fig_S3.2", caption = "Residual plot for linear model of abundance with normally distributed errors", display = FALSE)
fig_nums(name = "Fig_S3.3", caption = "Total Zooplankton abundance and modeled temperature dependence from negative binomial regression", display = FALSE)
fig_nums(name = "Fig_S3.4", caption = "Abundance of Daphnia and Copepods (Number / 10L) over all tanks and weeks.", display = FALSE)
fig_nums(name = "Fig_S3.5", caption = "Daphnia abundance with modeled temperature dependence from poisson regression; estimates and confidence intervals given in Table S3.3", display = FALSE)
fig_nums(name = "Fig_S3.6", caption = "Copepod abundance with modeled temperature dependence from poisson regression", display = FALSE)
fig_nums(name = "Fig_S3.7", caption = "Zooplankton body size (length) over all tanks and weeks.", display = FALSE)
fig_nums(name = "Fig_S3.8", caption = "Zooplankton body size (length) and modeled effects of predation", display = FALSE)
```

#### Section S3.1: Zooplankton Abundance data over whole experiment
```{r Total Zooplankton analysis, echo = FALSE}
data.N <- as_tibble(data) %>%
  group_by(Tank, trophic.level, week) %>%
  filter(trophic.level != 'P', week > 3) %>%
  dplyr::select(., Tank, trophic.level, week, invTT, average.temp, abundance.Daphnia, abundance.copepods, Daphnia.Copepod.Ratio, total.zoo.abundance.liter) %>%
  arrange(trophic.level, week) 

data.N$Nt <- 10*(data.N$total.zoo.abundance.liter) #b/c we observed ZP in 10 L samples. 
data.N$Dt <- 10*(data.N$abundance.Daphnia)
data.N$Ct <- 10*(data.N$abundance.copepods)
data.N$week <- as.factor(data.N$week)
data.N$Tank <- as.factor(data.N$Tank)
```

`r fig_nums("Fig_S3.1")`

```{r Fig_S3.1: Histogram ZP Abundance, echo=FALSE, fig.width=3, fig.height=3}
hist(data.N$Nt, main = " ")
```

```{r Testing ZP model options, echo = FALSE}
# first try: poisson regression
m1 <- glm(Nt ~ trophic.level + invTT, family="poisson", data=data.N)

## second try: lm random effects models with normally distributed errors
m2 <- lmer(Nt ~ invTT + trophic.level + (1|Tank), data = data.N)
#summary(m2)
#shapiro.test(resid(m2))
```



`r fig_nums("Fig_S3.2")`

```{r resid_plot_lm, echo=FALSE, fig.width=3,fig.height=3}
qqnorm(resid(m2))
qqline(resid(m2)) ## ok, shapiro test + this plot show that the linear model is not right.
```

```{r poison errors, echo = FALSE}
## third try: glm with poisson errors.
poismod <- glmmadmb(Nt ~ average.temp + trophic.level + (1|Tank), family = "poisson", data = data.N)
# for poisson analysis and plotting, this is helpful: https://stats.idre.ucla.edu/r/dae/poisson-regression/
# they point out that negative binomial for zero-inflated data is a generalized version of poisson, so I will follow these methods here for the nb model.

## test for overdispersion:
#overdisp_fun(poismod) 

# overdispersed, so:
nbinommod1 <- glmmadmb(Nt ~ invTT + trophic.level + (1|Tank), family = "nbinom", zeroInflation = T, data = data.N)
overdisp_fun(nbinommod1) ## no longer overdispersed
#summary(nbinommod1)

# proceed with alternate fixed effects models
nbinommod1a <- glmmadmb(Nt ~ trophic.level + (1|Tank), family = "nbinom", zeroInflation = T, data = data.N)
nbinommod1b <- glmmadmb(Nt ~ invTT + (1|Tank), family = "nbinom", zeroInflation = T, data = data.N)
nbinommod1c <- glmmadmb(Nt ~ 1 + (1|Tank), family = "nbinom", zeroInflation = T, data = data.N)

res <- model.sel(nbinommod1, nbinommod1a, nbinommod1b, nbinommod1c)
#anova(nbinommod1, nbinommod1b) # so proceed wtih nbionmmod1b
```


`r table_nums("Table_1")`
```{r Table_S1}
kable(res, digits=2, col.names = c('Int','T~wj~','Z~j~','df', 'logLik', 'AICc', 'd', 'w'))
```

```{r summarize best model}
#summary(nbinommod1b)
m1 <- nbinommod1b
r.est <- cbind(Estimate = coef(m1), se = stdEr(m1), 
            "Pr(>|z|)" = 2 * pnorm(abs(coef(m1)/stdEr(m1)), lower.tail=FALSE),
            LL = coef(m1) - 1.96 * stdEr(m1),
            UL = coef(m1) + 1.96 * stdEr(m1))
```


```{r plotting total zooplankton results}
### use model coefficients to estimate lines for later plotting; transformation in the negative binomial is log, so exponentiating the estimates reverses that. BUT, in this case we are interested in the response of the log (to get an Ea value) so I will not back transform, but instead plot on logged axes.

N.PZ <- function(x) { exp(fixef(nbinommod1b)[1] + fixef(nbinommod1b)[2]*x) }
N.PZL <- function(x) { exp(r.est[1,4] + r.est[2,4]*x) }
N.PZU <- function(x) { exp(r.est[1,5] + r.est[2,5]*x) }

data.N$week <- as.numeric(as.character(data.N$week))

N.plot2 <- ggplot(data = data.N, aes(x = -invTT, y = Nt, xmin = -40, xmax = -38.5, group = week, shape = as.factor(trophic.level), alpha = week)) +
  theme_bw() +
  geom_point(aes(group = as.character(week))) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),  
        legend.text = element_text(size = 6), 
        legend.title = element_text(size = 7), 
        legend.key = element_rect(fill = NA), 
        strip.text.y = element_blank(),
        strip.background = element_rect(colour="white", fill="white")) +
  #scale_alpha("week", guide = "none") +
  scale_shape_manual(guide = guide_legend(title = "Trophic Treatment"), values = c(1,2,22,23,8,15,16,17)) +
  ylab("Zooplankton abundance (ind/10L)") + 
  scale_x_continuous("Temperature (1/kTi)", sec.axis =sec_axis(~((1/(k*-.))-273), name = xlab))

N.plot3 <- N.plot2 +
  geom_smooth(data = subset(data.N, trophic.level == "PZ"), aes(x = -invTT, y = N.PZ(invTT)), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', size = 1.5) +
  geom_smooth(data = subset(data.N, trophic.level == "PZN"), aes(x = -invTT, y = N.PZ(invTT)), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'gray', size = 1.5, lty = 2) #+
  #geom_ribbon(data = subset(data.N, trophic.level == "PZ"), aes(ymin = N.PZL(invTT), ymax = N.PZU(invTT)), fill = "blue", alpha = .25)

ggsave("Fig4.png", width = 4, height = 4)
```

`r fig_nums("Fig_S3.3")`

```{r N_plot, fig.width=4,fig.height=4}
N.plot3
```

####
####
####


### Section S3.2: Daphnia and Copepods
`r fig_nums("Fig_S3.4")`

```{r Daphnia_abundance, fig.width=3,fig.height=3}
hist(data.N$Dt, main = "Daphnia / 10L")
hist(data.N$Dt, main = "Copepods / 10L")
#hist(data.N$Daphnia.Copepod.Ratio)
```

```{r Daphnia modeling}
##glm with poisson errors.
poismod.D <- glmmadmb(Dt ~ invTT + trophic.level + (1|Tank), family = "poisson", data = data.N)
#summary(poismod.D)

## test for overdispersion:
#overdisp_fun(poismod.D) ## not overdispersed, so stop here.

## model selection: [model not convering for Dt, but it is for D/10, so just doing that]
poismod.Da <- glmmadmb(abundance.Daphnia ~ 1 + invTT*trophic.level + (1|Tank), family = "poisson", data = data.N)
poismod.Db <- glmmadmb(abundance.Daphnia ~ 1 + invTT + trophic.level + (1|Tank), family = "poisson", data = data.N)
poismod.Dc <- glmmadmb(abundance.Daphnia ~ 1 + invTT + (1|Tank), family = "poisson", data = data.N)
poismod.Dd <- glmmadmb(abundance.Daphnia ~ 1 + (1|Tank), family = "poisson", data = data.N)
resD <- model.sel(poismod.Da, poismod.Db, poismod.Dc, poismod.Dd)
```

`r table_nums("Table_S3.2")`
```{r Daphnia table}
kable(resD, digits=2, col.names = c('Int','T~wj~','Z~j~','T~wj~*Z~j~','df', 'logLik', 'AICc', 'd', 'w'))
```

```{r Daphnia poisson model and model selection}
#summary(poismod.Db)
m1D <- poismod.Db
D.est <- cbind(Estimate = coef(m1D), se = stdEr(m1D), 
            "Pr(>|z|)" = 2 * pnorm(abs(coef(m1D)/stdEr(m1D)), lower.tail=FALSE),
            LL = coef(m1D) - 1.96 * stdEr(m1D),
            UL = coef(m1D) + 1.96 * stdEr(m1D))
```


`r table_nums("Table_S3.3")`
```{r Table S3.3: Daphnia coefs and confints}
kable(D.est, digits=2)
```



```{r Daphnia predicted values}
### use model coefficients to estimate lines for later plotting
D.PZ <- function(x) { exp(fixef(m1D)[1] + fixef(m1D)[2]*x) } # for trophic level 3
D.PZN <- function(x) { exp(fixef(m1D)[1] + fixef(m1D)[3] + fixef(m1D)[2]*x) } # for trophic level 3
```

```{r Daphnia plots}
D.plot2 <- ggplot(data = data.N, aes(x = -invTT, y = abundance.Daphnia, xmin = -40, xmax = -38.5, group = week, shape = as.factor(trophic.level), alpha = week)) +
  theme_bw() +
  geom_point(aes(group = as.character(week))) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),  
        legend.text = element_text(size = 6), 
        legend.title = element_text(size = 7), 
        legend.key = element_rect(fill = NA), 
        strip.text.y = element_blank(),
        strip.background = element_rect(colour="white", fill="white")) +
  #scale_alpha("week", guide = "none") +
  scale_shape_manual(guide = guide_legend(title = "Trophic Treatment"), values = c(1,2,22,23,8,15,16,17)) +
  ylab("Daphnia density (ind/L)") + 
  scale_x_continuous("Temperature (1/kTi)", sec.axis =sec_axis(~((1/(k*-.))-273), name = xlab))

D.plot3 <- D.plot2 +
  geom_smooth(data = subset(data.N, trophic.level == "PZ"), aes(x = -invTT, y = D.PZ(invTT)), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', size = 1.5) +
  geom_smooth(data = subset(data.N, trophic.level == "PZN"), aes(x = -invTT, y = D.PZN(invTT)), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'gray', size = 1.5, lty = 1)

#D.plot2 + geom_line(data=transform(data.N, abundance.Daphnia=(predict(poismod.Db))))

ggsave("Fig4a.png", width = 4, height = 4)
```



```{r Fig_S3.5: Daphnia abundance plot, fig.width=4,fig.height=4}
#`r fig_nums("Fig_S3.5")`
#D.plot3
```



```{r Copepod analysis}
##glm with poisson errors.
poismod.C <- glmmadmb(Ct ~ invTT + trophic.level + (1|Tank), family = "poisson", data = data.N)
#summary(poismod.C)

## test for overdispersion:
#overdisp_fun(poismod.C) ## overdispersed

nbC1 <- glmmadmb(Ct ~ invTT + trophic.level + (1|Tank), family = "nbinom", zeroInflation = F, data = data.N)
#summary(nbC1)
#overdisp_fun(nbC1)

## model selection: 
poismod.Ca <- glmmadmb(abundance.copepods ~ 1 + invTT*trophic.level + (1|Tank), family = "nbinom", zeroInflation = F, data = data.N)
poismod.Cb <- glmmadmb(abundance.copepods ~ 1 + invTT + trophic.level + (1|Tank), family = "nbinom", zeroInflation = F, data = data.N)
poismod.Cc <- glmmadmb(abundance.copepods ~ 1 + invTT + (1|Tank), family = "nbinom", zeroInflation = F, data = data.N)
poismod.Cd <- glmmadmb(abundance.copepods ~ 1 + (1|Tank), family = "nbinom", zeroInflation = F, data = data.N)
resC <- model.sel(poismod.Ca, poismod.Cb, poismod.Cc, poismod.Cd)
#summary(poismod.Cc)
```

`r table_nums("Table_S3.4")`

```{r Copepod abundance results}
kable(resC, digits=2, col.names = c('Int','T~wj~','Z~j~','T~wj~*Z~j~','df', 'logLik', 'AICc', 'd', 'w'))
```

```{r Copepod abundance model coefs}
m1C <- poismod.Cc
C.est <- cbind(Estimate = coef(m1C), se = stdEr(m1C), 
            "Pr(>|z|)" = 2 * pnorm(abs(coef(m1C)/stdEr(m1C)), lower.tail=FALSE),
            LL = coef(m1C) - 1.96 * stdEr(m1C),
            UL = coef(m1C) + 1.96 * stdEr(m1C))
```


`r table_nums("Table_S3.5")`
```{r Table_S3.5}
kable(C.est, digits = 2)
```


```{r Copepod plots, width = 4, height = 4}
### use model coefficients to estimate lines for later plotting
C.PZ <- function(x) { exp(fixef(poismod.Cc)[1] + fixef(poismod.Cc)[2]*x) } # for trophic level 3

#data.N$Chat <- predict(poismod.Cc)

C.plot2 <- ggplot(data = data.N, aes(x = -invTT, y = abundance.copepods, xmin = -40, xmax = -38.5, group = week, shape = as.factor(trophic.level), alpha = week)) +
  theme_bw() +
  geom_point(aes(group = as.character(week))) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),  
        legend.text = element_text(size = 6), 
        legend.title = element_text(size = 7), 
        legend.key = element_rect(fill = NA), 
        strip.text.y = element_blank(),
        strip.background = element_rect(colour="white", fill="white")) +
  #scale_alpha("week", guide = "none") +
  scale_shape_manual(guide = guide_legend(title = "Trophic Treatment"), values = c(1,2,22,23,8,15,16,17)) +
  ylab("Copepod density (ind/L)") + 
  scale_x_continuous("Temperature (1/kTi)", sec.axis =sec_axis(~((1/(k*-.))-273), name = xlab))

C.plot3 <- C.plot2 +
  geom_smooth(data = data.N, aes(x = -invTT, y = C.PZ(invTT)), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', size = 1.5)

ggsave("Fig4b.png", width = 4, height = 4)
```


```{r copepod abundance figure}
#`r fig_nums("Fig_S3.6")`
C.plot3
#ggsave("Dabundance.png", device = "png")
```

### Section S3.4: Zooplankton size analysis
```{r Size analysis}
sizes <- read.csv("../data/GarzkeSizes.csv")
#View(sizes)

sizes$week <- as.factor(sizes$week)
sizes$Tank <- as.factor(sizes$Tank)

sizes$taxon <- sizes$species
levels(sizes$taxon)[levels(sizes$taxon)== "calanoid"] <- "Copepod"
levels(sizes$taxon)[levels(sizes$taxon)== "cyclopoid"] <- "Copepod"
levels(sizes$taxon)[levels(sizes$taxon)== "Bosmina"] <- "Daphnia"
```

```{r}
data.S <- as_tibble(sizes) %>%
  group_by(Tank, trophic.level, week) %>%
  filter(trophic.level != 'P') %>%
  arrange(trophic.level, week) 
  #dplyr::select(., Tank, trophic.level, week, invTT, average.temp, abundance.Daphnia, abundance.copepods, Daphnia.Copepod.Ratio, total.zoo.abundance.liter) %>%
```

`r fig_nums("Fig_S3.7")`

```{r Fig_S3.7 Zooplankton size data, fig.width = 3, fig.height = 3}  
hist(data.S$size)
hist(log(data.S$size))
```

```{r size model}
## tried with untransformed data, and truncated models would not converge. So trying again with log transformed data. 
# first try: lm random effects models with normally distributed errors
m2 <- lmer(log(size) ~ invTT + trophic.level + (1|Tank), data = data.S)
#shapiro.test(resid(m2)) # very non-normal (both raw and log trasnformed)

# poisson regression
m1 <- glm(size ~ trophic.level + invTT, family="poisson", data=data.S)
#shapiro.test(resid(m1)) # very non-normal; probably need a zero-truncated poisson

#qqnorm(resid(m2)) # but not too bad; go ahead with this.
#qqline(resid(m2))

#m3 <- glmmadmb(size ~ invTT + trophic.level + (1|Tank), family = "poisson", data = data.S)
#shapiro.test(resid(m3)) # very non-normal

#m4 <- glmmadmb(size ~ invTT + trophic.level + (1|Tank), family = "truncnbinom1", data = data.S)
#shapiro.test(resid(m4)) # very non-normal
```


```{r size model comparison, echo = FALSE}
m2a <- lmer(log(size) ~ invTT*trophic.level*taxon + (1|Tank), REML = FALSE, data = data.S)
#summary(m2a)
#shapiro.test(resid(m2a))

m2b <- lmer(log(size) ~ I(-(invTT-mean(invTT)))*taxon + I(-(invTT-mean(invTT)))*trophic.level + (1|Tank), REML = FALSE, data = data.S)
m2j <- lmer(log(size) ~ I(-(invTT-mean(invTT)))*taxon + trophic.level + (1|Tank), REML = FALSE, data = data.S)
m2c <- lmer(log(size) ~ I(-(invTT-mean(invTT))) + trophic.level*taxon + (1|Tank), REML = FALSE, data = data.S)
m2d <- lmer(log(size) ~ I(-(invTT-mean(invTT))) + trophic.level + (1|Tank), REML = FALSE, data = data.S)
m2k <- lmer(log(size) ~ I(-(invTT-mean(invTT)))*trophic.level + (1|Tank), REML = FALSE, data = data.S)
m2m <- lmer(log(size) ~ I(-(invTT-mean(invTT)))*trophic.level + taxon + (1|Tank), REML = FALSE, data = data.S)
m2e <- lmer(log(size) ~ I(-(invTT-mean(invTT))) + taxon + (1|Tank), REML = FALSE, data = data.S)
m2l <- lmer(log(size) ~ I(-(invTT-mean(invTT)))*taxon + (1|Tank), REML = FALSE, data = data.S)
m2f <- lmer(log(size) ~ I(-(invTT-mean(invTT))) + (1|Tank), REML = FALSE, data = data.S)
m2g <- lmer(log(size) ~ trophic.level*taxon + (1|Tank), REML = FALSE, data = data.S)
m2h <- lmer(log(size) ~ taxon + (1|Tank), REML = FALSE, data = data.S)
m2i <- lmer(log(size) ~ trophic.level + (1|Tank), REML = FALSE, data = data.S)

resS <- model.sel(m2b, m2c, m2d, m2e, m2f, m2g, m2h, m2i, m2j, m2k, m2l, m2m)
#summary(m2g)
#m.avg <- model.avg(m2g)
```

```{r}
S.plot2 <- ggplot(data = data.S, aes(x = -invTT, y = log(size), xmin = -40, xmax = -38.5, group = week, shape = as.factor(trophic.level), alpha = week)) +
  theme_bw() +
  geom_point(aes(group = as.character(week))) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),  
        legend.text = element_text(size = 6), 
        legend.title = element_text(size = 7), 
        legend.key = element_rect(fill = NA), 
        strip.text.y = element_blank(),
        strip.background = element_rect(colour="white", fill="white")) +
  #scale_alpha("week", guide = "none") +
  scale_shape_manual(guide = guide_legend(title = "Trophic Treatment"), values = c(1,2,22,23,8,15,16,17)) +
  ylab("length (ln(cm))") + 
  scale_x_continuous("Temperature (1/kTi)", sec.axis =sec_axis(~((1/(k*-.))-273), name = xlab))

S.plot3 <- S.plot2 +
  geom_smooth(data = data.S, aes(x = -invTT, y = S(invTT)), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', size = 1.5)


```

\pagebreak

`r table_nums("Table_S3.8")`

```{r Table_S3.8: Size model comparison}
kable(resS, digits=2, col.names = c('Int','T~wj~','Tx','Z~j~','T~wj~*Tx','T~wj~*Z~j~','Tx*Z~j~', 'df', 'logLik', 'AICc', 'd', 'w'))
```


```{r zooplankton size coefficients}
Sd.PZ <- fixef(m2g)[1]
Sc.PZ <- fixef(m2g)[1] + fixef(m2g)[3]
Sd.PZN <- fixef(m2g)[1] + fixef(m2g)[2]
Sc.PZN <- fixef(m2g)[1] + fixef(m2g)[3] + fixef(m2g)[4]
confint(m2b) -> SizeInts

#df <- length(data.S$size)-(length(coef(m2g))+1)-1
#t.stat <- qt(0.975, df = df)
#D.l2 <- fixef(m2g)[1] - t.stat * sqrt(vcov(m2g)[1,1])
#D.u2 <- fixef(m2g)[1] + t.stat * sqrt(vcov(m2g)[1,1])
#C.l2 <- fixef(m2g)[1] + fixef(m2g)[3] - t.stat * sqrt(vcov(m2g)[1,1] + vcov(m2g)[3,3] + #2*vcov(m2g)[1,3])
#C.u2 <- fixef(m2g)[1] + fixef(m2g)[3] + t.stat * sqrt(vcov(m2g)[1,1] + vcov(m2g)[3,3] + 2*vcov(m2g)[1,3])

#S.est <- cbind(Estimate = c(fixef(m2g)[1], fixef(m2g)[1] + fixef(m2g)[3]), Lower = c(D.l2, C.l2), Upper = c(D.u2, C.u2))
S.est <- cbind(Daphnia = c(exp(Sd.PZ), exp(Sd.PZN)), Copepods = c(exp(Sc.PZ), exp(Sc.PZN)))
rownames(S.est) <- c("- Predators", "+ Predators")
```
`r table_nums("Table_S3.9")`

```{r Table_S3.9}
kable(S.est, digits = 2)
```



```{r size_plot}
S.plot <- ggplot(data = data.S, aes(x = -invTT, y = log(size), xmin = -40.2, xmax = -38.2)) +
  theme_bw() +
  theme(legend.position = "none") +
  geom_point(aes(group = as.character(Tank), color = as.character(trophic.level))) +
  facet_grid(.~taxon) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),  
        legend.text = element_text(size = 3), 
        legend.title = element_text(size = 3), 
        legend.key = element_rect(fill = NA), 
        strip.text.y = element_blank(),
        strip.background = element_rect(colour="white", fill="white")) +
  ylab("Zooplankton body size (log(mm))") + 
  scale_x_continuous("Mean Tank Temperature (1/kTi)", sec.axis = sec_axis(~((1/(k*-.))-273), name = "Temperature C"))

S.plot2 <- S.plot +
  geom_ribbon(data = subset(data.S[(data.S$taxon == 'Daphnia'),]), aes(ymin = Sd.PZ-SizeInts[1], ymax = Sd.PZ+SizeInts[1]), fill = "gray", alpha = .5) +
    geom_smooth(data = subset(data.S[(data.S$taxon == 'Daphnia'),]), aes(x = -invTT, y = Sd.PZ), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'blue', size = 1) +
   geom_ribbon(data = subset(data.S[(data.S$taxon == 'Copepod'),]), aes(ymin = Sc.PZ-SizeInts[1], ymax = Sc.PZ+SizeInts[1]), fill = "gray", alpha = .5) +  
  geom_smooth(data = subset(data.S[(data.S$taxon == 'Copepod'),]), aes(x = -invTT, y = Sc.PZ), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'blue', size = 1.5)
```

`r fig_nums("Fig_S3.8")`

```{r size plot}
S.plot2
```